SCM plan for a troubling company

### 2012-01-11 article.tex
gitignore modified

%opening
\title{Introducing SCM to a small company}
\author{Jonas Nolte, dt07jn1\\
David Everlöf, dt08de2\\
Tobias Petersen, et07tp3}

@@

In the identification process the different baselines must be identified. And more specifically who creates them, authorizes and verifies them, as well as the contents of them.

@@

>>>>

%opening
\title{SCM plan for a troubling company}
\author{Jonas Nolte, dt07jn1\\
David Everlöf, dt08de2\\
Tobias Petersen, et07tp3}

@@

In the identification process the different baselines must be identified. And more specifically who creates them, authorizes and verifies them, as well as the contents of them.\cite{cagan}

@@

The main idea behind configuration control is to achieve control of changes, what impact they'll have and their costs.

Since this company is relatively small, the extent of CCB and it's usage will be a somewhat limited in contrary to the general idea of a CCB.
The CCB consist of the normal lineup with: chairperson, secretary, members and specialists \cite{daniels}. We will select the project manager
to be the chairman and the secretary will be the configuration manager in the company. The project manager will appoint appropriate people to be
members of the CCB and specilists will be contacted on a ``when needed''-basis.

Not every change will be handled by the CCB in our case
